The Structure of Human Language Reflects Limitations of Working Memory

### 2019-04-25 paper-short.tex
revising

>>>>

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures-gdrive/theorem.png}
	\caption{The statement of the theoretical result.}\label{fig:results}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures-gdrive/tradeoff.png}
	\caption{}\label{fig:results}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures-gdrive/counterfactual-languages.png}
	\caption{Estimating chance by constructing counterfactual grammars and languages.}\label{fig:results}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures-gdrive/mi-distance.png}
	\caption{}\label{fig:results}
\end{figure}
